\section{Conclusion}

Knowledge based data processing is essential to address heterogeneous data originating from multiple sources in a distributed
system. It is also essential for the data to be processed in a distributed fashion over the network in large distributed 
systems. Distributed knowledge representattion over the web assumes significance in this context. There need to be a standard
scheme for knowledge representation, so that the distributed knowledge can be accessed and used by independently designed 
system components on the web. 
%
In this chapter, we have provided an introduction to the semantic web technology recommended by W3C, which provides starndardized 
methods for representation, interconnection and manipulation of web-based knowledge resources. In particular, we have discussed
RDF and SPARQL, which are the standard techniques for knowledge representation and query on the web. We have shown how knowledge
can be manipulated in a distributed fashion using those techniques. We have also reviewed application of knowledge based techniques  
in data fusion applications in distributed sensor networks.

As the distributed systems grow larger in size, there is a need to for intelligent system components that can work autonomously
without human intervention for prolonged period of time. These intelligent and autonomous system components should be able to
communicate and coordinate witheach other to realize the system goals. This leads to the concept distributed intelligence, realized 
with intelligent agent technology, which we shall review in the next chapter.


