\section*{Exercises}

\begin{enumerate}
	\item Represent the infobox information given in listing~\ref{list:knowledge:wiki-infobox} in RDF format.
	\item Identify all paths and schema paths in the RDF graphs presented in figure~\ref{fig:knowledge:rdf-dataset}.
	\item Draw the BGP for SPARQL query provided in listing~\ref{list:knowledge:sparql-1}, and identify the query results (matching 
		minimal subgraphs) in dataset depicted in figure~\ref{fig:knowledge:rdf-dataset}.
	\item This exercise involves creating and storing an RDF dataset and querying on it. 
		\begin{itemize}
			\item Download the citations for about 10 documents cited at the end of this chapter from ACM Digital library 
				(\url{dl.acm.org}) in bibtex format. 
			\item Write a program to parse the bibtex records and create 
				an RDF data-source containing the bibliographic entries. Note that there is no unique data model and
				you need to design your own, following the suggestions:
					\begin{itemize} 
						\item Treat authors, journals, conferences, etc. as resources, and represent them 
							as IRIs (not as literals).  
						\item Use standard vocabularies (e.g. Dublin Core (DCMI), Schema.net, SKOS, etc.)
							as far as possible, and define your own vocabulay, if absolutely needed. 
						\item You may skip some of the fields, but keep those required for your queries.
					\end{itemize}
			\item Download and install GraphDB Free version (\url{http://graphdb.ontotext.com/}) and import the data
				in the database.
			\item Express some queries, such as those provided below, in SPARQL, execute them on the database, and 
				verify the results.
				\begin{itemize}
					\item Given a document title, find it's bibliographic details (authors, year, journal, conference, 
						etc.).
					\item Given a document title, find all other documents written by it's authors.
					\item Given an author's name, find all his/her co-authors.
					\item Given a year, find the authors who published in that year.
				\end{itemize}
		\item Repeat the same experiment with Apache Jena (\url{https://jena.apache.org/}) TDB triple-store.
		\end{itemize}
	\item Implement the Bayesian distributed data integration algorithm discussed in isection~\ref{sec:knowledge:constrained} over
		Pregel's algorithm discussed in chapter~\ref{chap:bigdata}. Assume any arbitrary connections amongst the nodes.
\end{enumerate}
