
As the distributed systems grow, and are required to do more and more complex tasks, there appears a need for knowledge-based data 
processing. Knowledge is an abstraction and interpretation of the related data elements. In digital form, knowledge can be stored 
on different computing nodes distributed over the Internet. We have presented the methods for storing and processing distributed 
data items in the previous chapter. In this chapter, we shall review representation of the distributed knowledge and knowledge-based 
information processing.

\index{W3C} \index{World Wide Web Consortium|see {W3C}}
\index{W3C}
\index{distributed sensor network} \index{constrained systems}
The rest of the chapter is organized as follows. We begin with a common representation of distributed knowledge, and provide a 
few examples of large open distributed knowledge bases created with that representation. This is followed by techniques for 
querying the distributed knowledge so created. These technologies are collectively known as {\em semantic web} technologies, 
recommended by World Wide Web Consortium (W3C) for knowledge based systems on the web.
Going forward, we discuss methods for efficient query processing on knowledgebases using distributed data management and 
distributed computation techniques. Further, we move on to applications of knowledge based processing in distributed sensor 
networks, which represent very large distributed systems with constrained computational environment. 
Finally, we conclude the chapter with some salient observations and need for distributed intelligence in distributed systems.

We end this introduction with a note for the readers. Distributed knowledge processing is an interdisciplinary topic with an 
amalgamation of techniques from artificial intelligence and distributed computing. We consciously focus on the latter aspect
in this book, keeping the discussions on the former to a bare minimum, which is required for appreciating the requirements
and sets the context for the methods for distributed processing.

\input ./Knowledge/dknowledge.tex
\input ./Knowledge/ldata.tex
\input ./Knowledge/dquery.tex
\input ./Knowledge/data-fusion.tex
\input ./Knowledge/conclusion.tex
\input ./Knowledge/exercises.tex
